Evaluating urban greening scenarios for urban heat mitigation: a spatially-explicit approach

### 2020-12-04 reports/article.tex
mention validation and R2 of previous work, added recent plosone ref

The parameters of the model are set based on its calibration to the same study area in previous work \cite{bosch2020spatially}.
Finally, the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) values are derived from the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ is set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ is set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

@@

% 3. EVALUATE FUTURE SCENARIOS, COMPARE SPRAWL VS INFILL
% Additionally, we can use the approach to compare distinct urban expansion scenarios (e.g., compact, sprawl) \cite{lemonsu2015vulnerability,yang2016contrasting}, also landscape homogenization along the urban-rural gradient \cite{wang2020spatial}.
Despite the limitations noted above, a major advantage of the proposed approach is that it can be used to evaluate urban heat mitigation of synthetic scenarios.
The simulations presented in this article focus on spatially exploring the effects of an increase of the tree canopy cover, yet there is room for much more experimentation of this kind.
% For instance,
% For instance, the sampling approaches to select the transformed pixels explored above can be replaced by ad-hoc optimization procedures that aim at minimizing the exposure of the most vulnerable populations to critical heat thresholds.
On the one hand, the generic sampling approaches explored above can be extended to consider ad-hoc characteristics such as the spatial distribution of the population, and design optimization procedures with specific goals. For instance, the candidate pixels can be selected with the aim of minimizing the exposure of the most vulnerable populations to critical heat thresholds.
% The approach can be used as part of a broader decision support system to explore the trade-offs between ecosystem services provided by trees, perform weighted optimizations and map priority planting locations \cite{bodnaruk2017plant}.
More broadly, the approach can be used as part of decision support system to explore the trade-offs between ecosystem services provided by trees, perform weighted optimizations and map priority planting locations \cite{bodnaruk2017plant}.
% MAYBE: landscape ecology principals/network planning to ensure connectivity and the like? see \cite[page 766]{haaland2015challenges}
On the other hand, in line with recent studies \cite{lemonsu2015vulnerability,yang2016contrasting,trimmel2019thermal}, the approach could be applied to examine the impact of distinct urbanization scenarios such as densification and urban sprawl on air temperature and human exposure to extreme heat, under current conditions as well as future climate estimates, e.g., by changing the $T_{ref}$ or $UHI_{max}$ parameters.
Similarly, InVEST urban cooling model might be coupled with models of LULC change such as cellular automata in order to assess not only which scenarios are most desirable in terms of urban heat mitigation, but also which planning strategies might lead to them \cite{silva2008strategies,white2015modeling,bosch2019addressing}.
% Also to evaluate projected LULC maps (e.g., outputs of cellular-automata simulations \cite{bosch2019addressing})

>>>>

The parameters of the model are set based on its calibration to the same study area in previous work \cite{bosch2020spatially}, which reproduces the air temperature measurements of 11 monitoring stations (see \autoref{fig:monitoring-stations}) with a coefficient of adjustment ($R^2$) of 0.90 and a mean absolute error of 0.96$\degree$C.
Finally, the temperature values observed at these stations are used to set the values of the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) parameters. More precisely, $T_{ref}$ is set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ is set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

@@

% 3. EVALUATE FUTURE SCENARIOS, COMPARE SPRAWL VS INFILL
% Additionally, we can use the approach to compare distinct urban expansion scenarios (e.g., compact, sprawl) \cite{lemonsu2015vulnerability,yang2016contrasting}, also landscape homogenization along the urban-rural gradient \cite{wang2020spatial}.
Despite the limitations noted above, a major advantage of the proposed approach is that it can be used to evaluate urban heat mitigation of synthetic scenarios.
The simulations presented in this article focus on spatially exploring the effects of an increase of the tree canopy cover, yet there is room for much more experimentation of this kind.
% For instance,
% For instance, the sampling approaches to select the transformed pixels explored above can be replaced by ad-hoc optimization procedures that aim at minimizing the exposure of the most vulnerable populations to critical heat thresholds.
On the one hand, the generic sampling approaches explored above can be extended to consider ad-hoc characteristics such as the spatial distribution of the population, and design optimization procedures with specific goals. For instance, the candidate pixels can be selected with the aim of minimizing the exposure of the most vulnerable populations to critical heat thresholds.
% The approach can be used as part of a broader decision support system to explore the trade-offs between ecosystem services provided by trees, perform weighted optimizations and map priority planting locations \cite{bodnaruk2017plant}.
More broadly, the approach can be used as part of decision support system to explore the trade-offs between ecosystem services provided by trees, perform weighted optimizations and map priority planting locations \cite{bodnaruk2017plant,werbin2020tree}.
% MAYBE: landscape ecology principals/network planning to ensure connectivity and the like? see \cite[page 766]{haaland2015challenges}
On the other hand, in line with recent studies \cite{lemonsu2015vulnerability,yang2016contrasting,trimmel2019thermal}, the approach could be applied to examine the impact of distinct urbanization scenarios such as densification and urban sprawl on air temperature and human exposure to extreme heat, under current conditions as well as future climate estimates, e.g., by changing the $T_{ref}$ or $UHI_{max}$ parameters.
Similarly, InVEST urban cooling model might be coupled with models of LULC change such as cellular automata in order to assess not only which scenarios are most desirable in terms of urban heat mitigation, but also which planning strategies might lead to them \cite{silva2008strategies,white2015modeling,bosch2019addressing}.
% Also to evaluate projected LULC maps (e.g., outputs of cellular-automata simulations \cite{bosch2019addressing})
